Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-02 paper/ms.tex
update ms

\subsection{The importance of half-cycles}

The interval of half a cycle period could be significant in the
context of CQVs for two reasons.  The first is that for material on a
circular orbit viewed edge-on, it corresponds to the interval between
transit and secondary eclipse.  The second is that it also corresponds
to the interval over which half of the star's surface is visible.
Of the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a number
that seems greater than random seem to exhibit a preference for
showing dips or peaks that correspond to the half-cycle interval.

@@

Our observations provide a direct measurement of how often dips
``appear'' or ``disappear'', both due to sudden state-switches, and
due to more gradual, secular evolution.  For instance, LP~12-502
showed 3 ``state-switch'' events over the six months of available TESS
observations, during cycles 248-264, 299-315, and 1233-1247.  It is
plausible to imagine that these events correspond to either mass being
ejected from corotation, or perhaps being accreted onto the star.  In
any event, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
over the $\approx$$10^8$ years for which the CQV phenomenon is
observed, this yields a cumulative moved dust mass of
$10^{-4}\,M_\oplus$, which of order the Solar System's asteroid belt.
If the occulting material is gas, the masses involved would be of
order 100 times larger.

>>>>

\subsection{Are half-cycles important?}

The interval of half a cycle period could be significant in the
context of CQVs for two reasons.  The first is that for material on a
circular orbit viewed edge-on, it corresponds to the interval between
transit and secondary eclipse.  The second is that it also corresponds
to the interval over which half of the star's surface is visible.
Of the CQVs in Figures~\ref{fig:cqvs} and~\ref{fig:evoln}, a number
that seems greater than random might exhibit a preference for
showing dips or peaks that correspond to the half-cycle interval.

@@

Our observations provide a direct measurement of how often dips
``appear'' or ``disappear'', both due to sudden state-switches, and
due to more gradual, secular evolution.  For instance, LP~12-502
showed 3 ``state-switch'' events over the six months of available TESS
observations, during cycles 248-264, 299-315, and 1233-1247.  It is
plausible to imagine that these events correspond to either mass being
ejected from corotation, or perhaps being accreted onto the star.  In
any event, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
over the $\approx$$10^8$ years for which the CQV phenomenon is
observed, this yields a cumulative moved dust mass of
$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.
If the occulting material is gas, the masses involved would be of
order 100 times larger.
